---
title: "shiny-assignment"
author: "Suheng Yao"
date: "2024-11-15"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
library(microbenchmark)
library(reactable)
```
```{r}
ui <- fluidPage(
  selectInput("dataset", label = "Dataset", choices = ls("package:datasets")),
  verbatimTextOutput("summary"),
  tableOutput("table")
)
server <- function(input, output, session) {
  output$summary <- renderPrint({
    mb_summary <- microbenchmark(
      {
        dataset <- get(input$dataset, "package:datasets")
        summary(dataset)
      },
      times = 10
    )
    print(mb_summary)
    dataset <- get(input$dataset, "package:datasets")
    summary(dataset)
  })
  
  output$table <- renderTable({
    mb_table <- microbenchmark(
      {
        dataset <- get(input$dataset, "package:datasets")
        dataset
      },
      times = 10 # Number of times to repeat the benchmark
    )
    dataset <- get(input$dataset, "package:datasets")
    dataset
  })
}
shinyApp(ui, server)
```
The maximum running time is 588.7 ms, but the minimum running time is 79.2 ms, which means that there is a large difference in running time efficiency. Since mean is much larger than the median running time, the distribution of running time could be right skewed, indicating that there are more outliers and running times greater than median.

```{r}
ui <- fluidPage(
  selectInput("dataset", label = "Dataset", choices = ls("package:datasets")),
  verbatimTextOutput("summary"),
  tableOutput("table")
)
server <- function(input, output, session) {
  # Create a reactive expression
  dataset <- reactive({
    get(input$dataset, "package:datasets")
  })

  output$summary <- renderPrint({
    mb_summary <- microbenchmark(
      {
        summary(dataset())
      },
      times = 10
    )
    print(mb_summary)
    summary(dataset())
  })
  
  output$table <- renderTable({
    mb_summary <- microbenchmark(
      {
        dataset()
      },
      times = 10
    )
    print(mb_summary)
    dataset()
  })
}
shinyApp(ui, server)
```
It is clear that using dataset() makes the function run much faster because the maximum running time is only 230.6 ms. The reason may be related to dataset() function is using reactive programming, and it only runs the first time it is called and then it caches its result until it needs to be updated. Thus, there are no duplicated codes, and the get() function won't need to run every time when initiating a shiny app.

## 2.3.5

### Question 1

(a) verbatimTextOutput
(b) textOutput
(c) verbatimTextOutput
(d) textOutput

### Question 2
```{r}
ui <- fluidPage(
  plotOutput("plot", width = "400px")
)
server <- function(input, output, session) {
  output$plot <- renderPlot(plot(1:5), res = 96, height = 300,
                            width = 700, 
                            alt = "Five Random Numbers")
}
shinyApp(ui, server)
```

### Question3
```{r}
ui <- fluidPage(
  DT::DTOutput("table")
)

server <- function(input, output, session) {
  output$table <- DT::renderDataTable(
    mtcars,
    options = list(
      paging = FALSE,      
      searching = FALSE,   
      ordering = FALSE,    
      info = FALSE
    )
  )
}

shinyApp(ui, server)

```

### Question 4
```{r}
ui <- fluidPage(
  reactableOutput("table")
)

server <- function(input, output, session) {
  output$table <- renderReactable({
    reactable(
      mtcars,
      pagination = FALSE,       
      sortable = FALSE,         
      filterable = FALSE,       
      showPageSizeOptions = FALSE,
      bordered = TRUE,          
      striped = TRUE
    )
  })
}

shinyApp(ui, server)

```

## 3.3.6

### Question 1
```{r}
ui <- fluidPage(
  textInput("name", "What's your name?"),
  textOutput("greeting")
)
server1 <- function(input, output, server) {
  input$greeting <- renderText(paste0("Hello ", input$name))
}

server2 <- function(input, output, server) {
  output$greeting <- renderText(paste0("Hello ", input$name))
}

server3 <- function(input, output, server) {
  output$greeting <- renderText({
    paste0("Hello ", input$name)
  })
}

shinyApp(ui, server)
```
### Question 2

(1) a, b -> c -> e -> f
(2) x1, x2, x3 -> x; y1, y2 -> y; x, y -> z
(3) a -> b -> c -> d

### Question 3

Since range and var are also function names in R, Shiny may not know which function to run, and this may cause error.

## 4.8

### Question 2

When the two function positions get flipped, the code will first select the top 5 categories, putting the rest in "Others" category, and arrange them according to their frequencies.

### Question 3
```{r}
injuries %>%
  mutate(diag = fct_lump(fct_infreq(diag), n = input$n_rows)) %>%
  group_by(diag) %>%
  summarise(n = as.integer(sum(weight)))
```
Assume n_rows is the number defined by the user.

### Question 4
```{r}
narratives <- c(
  "The patient experienced severe pain in the left arm.",
  "The diagnosis revealed a fracture in the left wrist.",
  "A cast was applied to immobilize the fracture.",
  "The patient is advised to follow up in two weeks."
)

ui <- fluidPage(
  titlePanel("Step Through Narratives"),
  
  
  fluidRow(
    column(6, actionButton("prev_btn", "Previous")),
    column(6, actionButton("next_btn", "Next"))
  ),
  
  
  hr(),
  textOutput("narrative_text"))

server <- function(input, output, session) {
  
  current_narrative <- reactiveVal(1) 
  
  
  observeEvent(input$next_btn, {
    if (current_narrative() < length(narratives)) {
      current_narrative(current_narrative() + 1) 
    }
  })
  
  observeEvent(input$prev_btn, {
    if (current_narrative() > 1) {
      current_narrative(current_narrative() - 1)
    }
  })
  
  output$narrative_text <- renderText({
    narratives[current_narrative()]
  })
}

shinyApp(ui, server)

```





